Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
Predicate system over Set.
Add universal quantification.

Suppose $X$ a set. Define a \emph{predicate on $X$} to be a family of (proof-irrelevant) propositions. For any
function $f: X \to Y$, define $\reindex{P}{f}(x)$ iff $P(f(x))$ and $\directImage{P}{f}(y)$ iff there exists
$x = f(y)$ such that $P(x)$. Define $\mathcal{S}$ to be the predicate system over $\Set$ which assigns to any
set $X$ the set $\Pred(X)$ of propositions on $X$ ordered by implication, with $\top, \meet, \join$ and
$\residual$ defined pointwise.

>>>>

Suppose $X$ a set. Define a \emph{predicate on $X$} to be a family of (proof-irrelevant) propositions. For any
function $f: X \to Y$, define $\reindex{P}{f}(x)$ iff $P(f(x))$ and $\directImage{P}{f}(y)$ iff there exists
$x$ such that $f(x) = y$ and $P(x)$. Define $\mathcal{S}$ to be the predicate system over $\Set$ which assigns
to any set $X$ the set $\Pred(X)$ of propositions on $X$ ordered by implication, with $\top, \meet, \join$ and
$\residual$ defined pointwise and universal quantification defined as $\forall_Y(P)(x)$ iff $P(x,y)$ for all
$y \in Y$.
